% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Alexander J. Norton}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{}


\begin{flushleft}
{\large\bf Alexander J. Norton}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 2422 Nottingham Drive, Falls Church, VA 22043 \\
\hfill (571)-405-0833\\
\hfill alexnorton@vt.edu 
\end{flushright} 

\opening{Dear Hiring Professional,} 
 


\noindent I am excited and passionate about working as a 
software developer for Khan Academy.  Salman Khan's mission to provide a free education
anywhere inspired me to create my own Youtube channel.  This channel taught Computer Science concepts.  Through over 250 videos, I was able to help others around the world while improving my ability to 
communicate clearly and effectively to an audience.  I received rave reviews from my users.  As a result, my subscription rate went from 400 to 1,200.

 \noindent I am interested in working for Khan Academy for two reasons.  The first reason is that Khan Academy wants to help people; Khan Academy is non profit.  I believe that by helping others we discover ourselves.  When I was a Teacher Assistant in college, facilitating intro to Python courses, it brought me great satisfaction to know I helped someone else jump over a hurdle to achieve their goals.  The second reason for wanting to work at Khan Academy as a software engineer is the challenge it presents.  Khan Academy has the huge task of making online education reputable around the world.  This will require solving problems that have never been tackled before.  In my senior capstone course, my group and I tackled a problem that involved using Hadoop to easily share resources.  The goal was to execute map reduce jobs using cluster shared resources.  In this project, we had to think outside the box to figure out how we could easily develop an executable and virtual machine that would spin up a Hadoop cluster on the fly.  I thoroughly enjoyed working this intricate problem within a team environment.  


\noindent As a software developer, I have dabbled in my many languages.  I used Ruby to make my Blog and personal website.  I learned Coffeescript to write less code and to make my sites more responsive.  I love using Git to keep my software maintainable and Vim to speed up my workflow.  You never stop learning in life, it is an endless cycle.  I would consider it a great honor to grow as a professional at Khan Academy and support its mission to make education available to everyone.

\noindent I will be studying abroad in Europe for the next couple of months, please contact my at your earliest convenience using my email address.

\closing{Sincerely yours,} 
 

 


\end{letter}
 

\end{document}






