% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass{my_cv}

% adjust the page margins
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file

\quote{Seeking a position as a Full Stack Developer}

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
%-----       letter       ---------------------------------------------------------
% recipient dat
\newcommand{\companyName}{CIA} % use a space at the end to make things easier below
\newcommand{\jobTitle}{Software Engineer }
\recipient{\companyName \ Recruitment}{\jobTitle position }
\date{\today}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle


I am extremely interested in the Software Engineer position.

MININIUM QUALIFICATIONS

I fit all the required qualifications and most of the desired.  I have a Computer Science Degree from Virginia Tech with a 3.8 GPA.

I have knowledge of Computer Science fundamentals in object oriented design, data structures, algorithm design, problem design, and complexity analysis.  I have knowledge of Windows, Linux, mobile operating systems, and SDKs.


I have experience in the following areas which you require.  In college, I wrote memory allocators (malloc) and operating systems in C, flushed out my linux environment, and have developed Android and iOS apps as a freelance developer.

I have experience in documenting all my work and publishing clear code.

As a developer at IBM, I learned how to work under an agile paradigm with weekly Scrums, that helped manage ever changing requirements for software projects.  I worked on a mobile application called Watson Workspace, contributing largely to the notifications and paging system upon opening the mobile application.  I was also responsible for the testing and deployment of my own code.  I also learned how to use the new iOS programming language, Swift, while on the job and with no loss of efficiency.

DESIRED QUALIFICATIONS

Although I do not posess a masters degree in Computer Science, I am willing to obtain one if necessary.

I have experience in multiple operating systems including Linux, macOS, and Windows.

I have experience in cryptographic principles, I took several cryptographic courses in college.  I also have experience in reverse engineering software and test driven development.  I understand wireless networks but do not have experience working with them.  I am willing to gain the experience if necessary.  Although I do not have systems engineer experience, I would be interested in acquiring it.

\iffalse
I love teaching, I started a Youtube channel in 2011, Apple Juice Teaching, that has over 1,000,000 views and 5,000 loyal subscribers.  I loved teaching everyone how to code and how to set up there development environment.  I was a teaching assistant for two years at Virginia Tech and had hands-on experience working with students and planning lessons with the teachers.  Nothing brings me more pleasure than helping students learn.

I love C programming.  My time at Virginia Tech made me very fluent in C and Linux.  I made a shell implementation, wrote our own malloc implemention, and a web server.  Learning how to debug, read assembly, weally taught me what object oriented programming languages are built on and taught me a core understanding of computer science.  I also took a multi-threading class that extensively covered p threads.  I also made a Youtube channel which taught C programming to any public user.

I have experience as an entrepreneur running my own website.  I learned how to use test driven development with Ruby on Rails with the database Postgres.  I learned how to use components of AWS, such as S3 and SES.  Writing all the software on my end taught me how to manage code and the importance of testing.  The importance of team work can not be understated at any company, a rising tide lifts all boats in the pier.
\fi

Computer programming and the opportunity to serve my country are my passions.  I am enthusiastic about expanding my
knowledge of programming, and embarking on new challenges.  In addition, I
believe I have a lot to offer \companyName \ in terms of programming expertise and
I am excited about the prospect of working for you.

Thank you for your consideration.  I look forward to meeting you to discuss how
I can support the mission of \companyName.

\makeletterclosing
%\clearpage\end{CJK*}% if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}
